---
title: "Analysis Brain sizes"
output:
  html_document:
    df_print: paged
---
```{r,echo=FALSE,message=FALSE}
library(tidyverse)
library(knitr)
```

Read in data from an sof project on 100 participants. Measured variables are brain size, head size, and gender.

```{r}
my_data<-read.csv("https://osf.io/4zbx2/download")
```

Calculate means and print a table.


```{r}
my_data_mean <- 
  my_data %>% 
  group_by(SEX) %>% 
  summarise(mean_BV = mean(BRAIN_VOLUME),
            sd_BV = sd(BRAIN_VOLUME))
kable(my_data_mean,digits = 1)
```

For distributional information and outlier detection see boxplot below:

```{r}
p_1<-ggplot(aes(y=BRAIN_VOLUME,x=SEX),data=my_data)+geom_boxplot()+theme_classic()+
  geom_jitter(width=.1,alpha=0.5)
print(p_1)
```

Males have a larger brain than females, hmm tempting thought, but how about correcting for head size

```{r}
my_data <-
  my_data %>% 
  mutate(rel_BV = BRAIN_VOLUME/HEAD_SIZE)

p_2<-ggplot(aes(y=rel_BV,x=SEX),data=my_data)+geom_boxplot()+theme_classic()+
  geom_jitter(width=.1,alpha=0.5)
print(p_2)
```

Ok, now for some statistics and linear regression, etc...




